Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex

### 2019-03-29 Manuscript.Rmd
added the extra permutation values (at 5k now)

``` {r Meta-analysis permutation, echo=FALSE, message = FALSE, cache = TRUE}
# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC
Yeo_labels <- c("L_25_ROI",
              "L_OFC_ROI",
              "L_10v_ROI",
              "R_25_ROI",
              "R_OFC_ROI",
              "R_10v_ROI",
              "L_s32_ROI",
              "L_RSC_ROI",
              "R_RSC_ROI",
              "R_23d_ROI",
              "R_d23ab_ROI",
              "R_31a_ROI",
              "R_31pv_ROI",
              "R_31pd_ROI",
              "R_7m_ROI",
              "R_v23ab_ROI",
              "R_p24_ROI",
              "R_d32_ROI",
              "R_9m_ROI",
              "R_p32_ROI",
              "R_a24_ROI",
              "R_10r_ROI",
              "R_10d_ROI",
              "L_23d_ROI",
              "L_d23ab_RO",
              "L_31a_ROI",
              "L_31pv_ROI",
              "L_31pd_ROI",
              "L_7m_ROI",
              "L_v23ab_ROI",
              "L_p24_ROI",
              "L_d32_ROI",
              "L_9m_ROI",
              "L_p32_ROI",
              "L_a24_ROI",
              "L_10r_ROI",
              "L_10d_ROI",
              "R_s32_ROI",
              "R_9a_ROI",
              "L_PCV_ROI")

@@

  # reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
  nPerms <- 1000

@@

  # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
  significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist, 0.95))

}
# results!
# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DMN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.01)
# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DMN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p < 0.05, R: p < 0.0001)
# v23 right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
# null 95th-q chi <- 9.11 (varies; this was done ith 100 but resembles the 5k one)

``` {r ROI computation (overlapping: DELETE), echo=FALSE, message = FALSE}
#TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
## ROI definition
# First, load the raw count csv files
valCounts <- read.csv2('decCounts.csv', sep = ",")
dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")

# Then, get the means of the counts per domain, both within/outside the search space
# This is to get a broad estimate of the average report amounts in the literature
tempBoot <- bootstrap(valCounts$Counts)
BV <- round(mean(tempBoot))
BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
tempBoot <- bootstrap(dmnCounts$Counts)
BD <- round(mean(tempBoot))
BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
rm(tempBoot)

# Now select only the ROIs from Yeo et al (TEMP)
valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords

# Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
# than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
for (i in seq(valCounts$Counts)) {
  indx <- valCounts$Counts[i]
  tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
  valCounts$Chi[i] <- tempTest$statistic
  valCounts$pVal[i] <- tempTest$p.value
}
for (i in seq(dmnCounts$Counts)) {
 indx <- dmnCounts$Counts[i]
 tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
 dmnCounts$Chi[i] <- tempTest$statistic
 dmnCounts$pVal[i] <- tempTest$p.value
}
# Retain only the significant parcels
t1 <- valCounts$Label[valCounts$pVal < 0.05]
t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
# Remove hemispheric references
t1 <- unique(substring(t1,2))
t2 <- unique(substring(t2,2))
# Labels to put in text
dmnLbls <- gsub("ROI","", t2)
dmnLbls <- gsub("_","", dmnLbls)
valLbls <- gsub("ROI","", t1)
valLbls <- gsub("_","", valLbls)

#bothLbls <- dmnLbls[dmnLbls %in% valLbls] # This part is just for reference, as the labels are loaded from a file
# final overlap
# And get the set of overlapping areas between literatures
# This is missing some cingulate and PFC areas, and adds V2.
# However, we can say that we are filling in the gap for completeness,
# and removing V2 because it's demonstrably irrelevant.
#bothLbls <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
# You could also try to permute the allocation of reports per literature,
# and then perform a chi-squared per parcel. Get the max stat per iteration.
# Now you have your null distribution.

@@

Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the significant differences between domains. The 95th percentile of the permuted chi-squared distribution was 9.11. Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DMN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.034; Right: observed $\chi^2$ = 18.89, *p* < 0.0001). The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.018; **TODO: ADD LEFT**). There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.014; Right: observed $\chi^2$ = 12.83, *p* = 0.014); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum. No toher parcels were preferentially implicated in valuation relative to DMN. We therefore selected area 7m as an interpretable, bilateral reference point for labeling DMN and non-DMN communities in the analyses that follow. We note that area 7m has been found to not partake in DMN in previous work [@AndrewsHanna2010]. However, we adhere to the nomenclature established by [@Glasser2016], whose area 7m is positioned considerably more ventrally and is well contained within canonical DMN.

@@

>>>>

``` {r Meta-analysis permutation, echo=FALSE, message = FALSE, cache = TRUE}
# Glasser parcels contained in Yeo's 17-net DMN and limbic networks on the medial cortical wall
Yeo_labels <- c("L_25_ROI",
              "L_OFC_ROI",
              "L_10v_ROI",
              "R_25_ROI",
              "R_OFC_ROI",
              "R_10v_ROI",
              "L_s32_ROI",
              "L_RSC_ROI",
              "R_RSC_ROI",
              "R_23d_ROI",
              "R_d23ab_ROI",
              "R_31a_ROI",
              "R_31pv_ROI",
              "R_31pd_ROI",
              "R_7m_ROI",
              "R_v23ab_ROI",
              "R_p24_ROI",
              "R_d32_ROI",
              "R_9m_ROI",
              "R_p32_ROI",
              "R_a24_ROI",
              "R_10r_ROI",
              "R_10d_ROI",
              "L_23d_ROI",
              "L_d23ab_RO",
              "L_31a_ROI",
              "L_31pv_ROI",
              "L_31pd_ROI",
              "L_7m_ROI",
              "L_v23ab_ROI",
              "L_p24_ROI",
              "L_d32_ROI",
              "L_9m_ROI",
              "L_p32_ROI",
              "L_a24_ROI",
              "L_10r_ROI",
              "L_10d_ROI",
              "R_s32_ROI",
              "R_9a_ROI",
              "L_PCV_ROI")

@@

  # reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
  nPerms <- 5000

@@

  # ROIs that survived the threshold based on Chi-squared value 
  significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist, 0.95))

}
# results!
# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DMN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.005)
# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DMN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p = 0.02, R: p < 0.0001)
# v23ab right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
# v23ab left (proportion sv = 0.16; proportion DMN = 0.32, chi = 8.25, p = 0.06)
# null 95th-q chi <- 8.87 (varies; this was done ith 100 but resembles the 5k one)

@@

Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the significant differences between domains. The 95th percentile of the permuted chi-squared distribution was 8.87. Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DMN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.029; Right: observed $\chi^2$ = 18.89, *p* < 0.001). The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.011; Left: observed $\chi^2$ = 8.25, *p* = 0.067). There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.005; Right: observed $\chi^2$ = 12.83, *p* = 0.005); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum. No toher parcels were preferentially implicated in valuation relative to DMN. We therefore selected area 7m as an interpretable, bilateral reference point for labeling DMN and non-DMN communities in the analyses that follow. We note that area 7m has been found to not partake in DMN in previous work [@AndrewsHanna2010]. However, we adhere to the nomenclature established by [@Glasser2016], whose area 7m is positioned considerably more ventrally and is well contained within canonical DMN.

@@

```{r Extra examples (supplemental fig 1), out.width = "50%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings, with their binarized forms. A common organizational principle is visible, even though it shifts topographically across individuals."}
include_graphics("./Images/extra_examples.png")
```

```{r ARI Comparison (supplemental fig 2), out.width = "50%", fig.align = "center", fig.cap = "Example of a day-to-day comparison using ARI for two subjects (100307 and 100408). This reflects how qualitatively similar, individual-specific partitionings can have relatively low values, and how partitionings across individuals are much closer to chance (i.e. 0)"}
include_graphics("./Images/ARI_comparison.png")
```
